Estimating the genome-wide contribution of selection to temporal allele frequency change

### 2020-05-14 manuscript/manuscript.tex
ms updates

  \caption{Mean temporal covariance ($\cov(\Delta p_5, p_t)$, with $t$ varying
    across the x-axis) across 30 replicate simulations (light gray points are
    before the onset of selection; dark gray points are after selection
    begins), under different Gaussian stabilizing selection with optima shift
  regimes. The solid red line is a loess-smoothed average of these points.}

>>>>

  \caption{Mean temporal covariance ($\cov(\Delta p_5, \Delta p_t)$, with $t$ varying
    across the x-axis) across 30 replicate simulations (light gray points are
    before the onset of selection; dark gray points are after selection
    begins), under different Gaussian stabilizing selection with optima shift
  regimes. The solid red line is a loess-smoothed average of these points.}
